### 2014-10-24 intro.tex
Minor edits

To address these issues, we introduce Quelea, a declarative programming system
for eventually consistent data stores. Quelea's programming model is built
around operation-based Commutative Replicated Data Types (CRDTs)
~\cite{shapiroCRDT}. The state of an abstract data type in Quelea is modeled as
a replicated \emph{append-only} log storing the history of all available
\emph{update} operations\footnote{Available at each replica. Different replicas
may have different logs as not all updates would have propagated to every
replica.} performed on the data type . For instance, the state of a replicated
counter ADT is stored on all replicas as a log of \emph{increment} and
\emph{decrement} operations performed on the counter. An operation that indends
to read the current value the counter at a replica only has to \emph{fold} over
the history log at that replica. Our key observation is that under this model,
consistency requirements of a replicated data type operation (eg:
\emph{decrement}) can be expressed effectively in terms of assertions on
\emph{membership} property of logs at various replicas. Quelea makes use of this
observation to introduce a simple \emph{contract language} that is nevertheless
capable of expressing fine-grained application-level consistency properties.
The contract language is made up of a couple of primitive relations, namely
\emph{visibility} and \emph{session order}, and a carefully choosen set of
logical operators. Quelea expects application programmer to use the contract
language to describe the set of legal executions allowed over the replicated
data types.  
% The executions descriptions are similar to the high-level axiomatic
% description of relaxed memory models~\cite{Demange2013}.
Subsequently, a contract enforcement system logically analyses contracts using
an SMT solver~\cite{z3} and automatically tags each operation with the weakest
store-level consistency guarantee that is required to satisfy application-level
consistency requirements. In addition, the system statically reports an error if
the given application-level consistency property cannot be satisfied by the
store.

>>>>

To address these issues, we introduce \name, a declarative programming system
for eventually consistent data stores. \name's programming model is built around
operation-based Commutative Replicated Data Types (CRDTs) ~\cite{shapiroCRDT}.
The state of an abstract data type in \name is modeled as a replicated
\emph{append-only} log storing the history of \emph{update} operations performed
on the data type . For instance, the state of a replicated counter ADT is stored
on all replicas as a log of \emph{increment} and \emph{decrement} operations
performed on the counter. An operation that indends to read the current value
the counter at a replica only has to \emph{fold} over the history log at that
replica. Our key observation is that under this model, consistency requirements
of a replicated data type operation (eg: \emph{decrement}) can be expressed
effectively in terms of assertions on \emph{membership} property of logs at
various replicas. \name makes use of this observation to introduce a simple
\emph{contract language} that is nevertheless capable of expressing fine-grained
application-level consistency properties.  The contract language is made up of a
couple of primitive relations, namely \emph{visibility} and \emph{session
order}, and a carefully choosen set of logical operators. \name expects
application programmer to use the contract language to describe the set of legal
executions allowed over the replicated data types.  
% The executions descriptions are similar to the high-level axiomatic
% description of relaxed memory models~\cite{Demange2013}.
Subsequently, a contract enforcement system logically analyses contracts using
an SMT solver~\cite{z3} and automatically tags each operation with the weakest
store-level consistency guarantee that is required to satisfy application-level
consistency requirements. In addition, the system statically reports an error if
the given application-level consistency property cannot be satisfied by the
store.
